% \documentclass[german,bachelor,mlu]{webisthesis}
% \documentclass[german,master,buw]{webisthesis}
%
% Non-default programme
% ---------------------
\documentclass[english,master,buw]{webisthesis}\global\thesisprogramme{Computer Science for Digital Media}
% \documentclass[english,master,buw]{webisthesis}\global\thesisfrontpagefaculty{Faculty of Civil Engineering/Faculty of Media}\global\thesisprogramme{Digital Engineering}
% \documentclass[german,bachelor,buw]{webisthesis}\global\thesisprogramme{Informatik\\Schwerpunkt Medieninformatik}
% \documentclass[german,bachelor,buw]{webisthesis}\global\thesisprogramme{Informatik\\Schwerpunkt Security and Data Science}
%
% When you change the language, pdflatex may halt on recompilation.
% Just hit enter to continue and recompile again. This should fix it.


%
% Values
% ------
\ThesisSetTitle{Teaching Queer Code: Educating Computer Science under Social Aesthetics}
\ThesisSetKeywords{masters thesis, queer, computer science} % only for PDF meta attributes
\ThesisSetLocation{Weimar, Germany} 

\ThesisSetAuthor{Artur Solomonik}
\ThesisSetStudentNumber{115715}
\ThesisSetDateOfBirth{10}{01}{1997}
\ThesisSetPlaceOfBirth{Tscherepowez}

% Supervisors should usually be Professors from the candidate's university. A second supervisor is not always needed. 
\ThesisSetSupervisors{Britta Schulte, Prof.\ Dr.\ Eva Hornecker}

\ThesisSetSubmissionDate{31}{2}{2022}

%
% Suggested Packages
% ------------------
\usepackage[sort&compress]{natbib}
%   Allows citing in different ways (e.g., only the authors if you use the
%   citation again within a short time).
%
\usepackage{booktabs}
%    For tables ``looking the right way''.
%
% \usepackage{tabularx}
%    Enables tables with columns that automatically fill the page width.
%
% \usepackage[ruled,algochapter]{algorithm2e}
%    A package for pseudo code algorithms.
%
% \usepackage{amsmath}
%    For tabular-style formatting of mathematical environments.
%

\usepackage{fontawesome}
%    For lots of awesome glyphs: https://mirror.physik.tu-berlin.de/pub/CTAN/fonts/fontawesome/doc/fontawesome.pdf

%
% Commenting (by your supervisor)
% -------------------------------
\usepackage{xcolor}
\usepackage{soul}
\newcommand{\bscom}[2]{%
  % #1 Original text.
  % #2 Replacement text.
    \st{\scriptsize\,#1}{\color{blue}\scriptsize\,#2}%
  }

% Create links in the pdf document
% Hyperref has some incompatibilities with other packages
% Some other packages must be loaded before, some after hyperref
% Additional options to the hyperref package can be provided in the braces [], like in
% \usehyperref[backref] % This will add back references in the bibliography that some people like ... some don't ... so better ask your supervisor ;-)
\usehyperref

\begin{document}
\begin{frontmatter}
\begin{abstract}
Creating software is closely tied to overcoming knowledge gaps between peers, automating busy work and improving code bases. The underlying processes function under a collective effort to maximize profit. With a multitude of ever-growing research tracks, the creative possibilities and social discourses seem diverse and fruitful. This promise, however, is challenging to upkeep as the industrial complex highly relies on the labor of writing code in the most effective ways possible. Technical evolution is rarely discussed on its ethics and politics during education, while the people affected by it do not get the time and resources to build digital fluency. The need for software developers and educational imbalance paint a narrative of the powerful and future-shaping developer. Learning resources closely relate to learning specific programming languages or frameworks, understanding the principles of code delivery, and working effectively in corporate teams. Swiftly, the potential of an unexplored medium such as code becomes an instrument for the industry, rather than subject to critical analysis and playing. What seems to be an opportunity to shape ideas in ways unimagined, becomes a commodity that is ought to be taught by the complex power dynamics of the cisheteropatriarchy. \\ \\
Computer science research groups, art collectives and (cyber-)feminist institutions embrace the idea of queering coding and standing up for the notions of creative processes in technology. Understanding the prevalent power of soft- and hardware and the ones who shape it, individuals can be educated on the focus of computer science by introducing feminist ideas on approaching the medium. Forming a collective consciousness on the impact of the medium code and applying it in technology even outside the generative context enables novel interactions with technology and the people influenced by it. With that in mind, while this thinking saw its implementation in coding projects with children, university courses, teaching resources, public art installations and video games already, digital, independent learning platforms and respective online infrastructure remains mostly unexplored.  \\ \\
In my thesis, I present an online education platform for exploring the principles of computer science, its societal implications and implementations in art, culture and prose. It is to show that by teaching creative code through a feminist gaze, people can critically comprehend the ideas of computer science. Based on the principals of Aesthetic Programming, alongside a corpus of resources from leading research on creative programming and curated guides, I provide an editor environment to build pseudocode through the possibilities of digital internet art. Over the course of two weeks, individuals work on their own programs while reflecting on their works and ideas. Through a probe study, and an interview, the individuals' assessment on their personal growth in the field will reveal the potential on teaching queer code. 
\end{abstract}

\tableofcontents

% \chapter*{Acknowledgements} % optional
% I thank the authors of the webisthesis template for their excellent work!

% \listoffigures % optional, usually not needed

% \listoftables % optional, usually not needed

% \listofalgorithms % optional, usually not needed
%    requires package algorithm2e

% optional: list of symbols/notation (e.g., using the nomencl package) but usually not needed
\end{frontmatter}

\include{introduction}
\include{background}
\include{methodology}
\include{results}
\include{discussion}
\include{threats}

\include{appendixA}

% Bibliography
\bibliographystyle{plainnat} % requires package natbib. An alternative is apalike
\bibliography{literature}    % load file literature.bib

\end{document}

